---
title: "Untitled"
author: "Steven Dutt Ross"
date: "5 de julho de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# https://github.com/bwlewis/crosstool
```

# Using ‘receiver’ to debug crosstalk key state

```{r}
library(crosstalk)
library(crosstool)
library(htmltools)
library(d3scatter) # devtools::install_github("jcheng5/d3scatter")

x = iris[sample(150, 50), ]
rownames(x) = NULL
x$key = state.name
sd = SharedData$new(x, key=~key)
d1 = d3scatter(sd, x=~Petal.Length, y=~Petal.Width, color=~Species, width="100%")
d2 = d3scatter(sd, x=~Sepal.Length, y=~Sepal.Width, color=~Species, width="100%")

rx = crosstool(sd, "receiver",  html="<span style='font-size:14pt; word-wrap:break-word;'/>", value="innerText", width="100%")
bscols(d1, d2, rx, widths=c(4,4,4))
```

# Using ‘transmitter’ to set initial selection handle state for a crosstalk group

This is one way to address the discussion in https://github.com/rstudio/crosstalk/issues/16.

```{r}
library(crosstalk)
library(crosstool)
library(htmltools)
library(d3scatter)

x = iris[sample(150, 50), ]
rownames(x) = NULL
x$key = state.name
sd = SharedData$new(x, key=~key)
d1 = d3scatter(sd, x=~Petal.Length, y=~Petal.Width, color=~Species, width="100%")
d2 = d3scatter(sd, x=~Sepal.Length, y=~Sepal.Width, color=~Species, width="100%")

rx = crosstool(sd, "receiver",  html="<span style='font-size:14pt; word-wrap:break-word;'/>", value="innerText", width="100%")

# Make an initial random selection and use the 'init' option
i = sample(state.name, 10)
tx = crosstool(sd, "transmitter", init=i)

bscols(d1, d2, rx, tx, widths=c(4,4,4,0))
```

# Using a transceiver to set initial filter handle state

Use the init and reset arguments of the transceiver to set up an initial filter handle state and then reset it when other filters are activated. Based on the filter example from https://rstudio.github.io/crosstalk/using.html.

```{r}
library(crosstalk)
library(htmltools)
library(crosstool)
library(d3scatter)

shared_mtcars <- SharedData$new(mtcars)
# debug the key state to show active filter keys
sp = crosstool(shared_mtcars, "receiver", "<span style='font-size:14pt; word-wrap:break-word;'/>", value="innerText", channel="filter")
# Make an initial random filter and use the 'init' option
i = sample(rownames(mtcars), 10)
tx = crosstool(shared_mtcars, "transceiver", init=i, channel="filter", reset=rownames(mtcars))

bscols(widths = c(3,NA,NA),
  list(
    filter_checkbox("cyl", "Cylinders", shared_mtcars, ~cyl, inline = TRUE),
    filter_slider("hp", "Horsepower", shared_mtcars, ~hp),
    filter_select("auto", "Automatic", shared_mtcars, ~ifelse(am == 0, "Yes", "No"))
  ),
  list(d3scatter(shared_mtcars, ~wt, ~mpg, ~factor(cyl), width="100%", height=250), sp),
  list(d3scatter(shared_mtcars, ~hp, ~qsec, ~factor(cyl), width="100%", height=250), tx)
)
```


