---
title: "Bootstrap alerts in R Markdown"
author: "David A. Selby"
output:
  html_document:
    keep_md: yes
    code_download: yes
---

FONTE: https://selbydavid.com/vignettes/alerts.html#

The default errors, warnings and messages in R Markdown are OK, but HTML output could look so much better in HTML, considering the templates use Twitter Bootstrap by default.

Let's see what we can do instead with a few CSS classes!

```{r setup, include=FALSE}
knitr::knit_hooks$set(
   error = function(x, options) {
     paste('\n\n<div class="alert alert-danger">',
           gsub('##', '\n', gsub('^##\ Error', '**Error**', x)),
           '</div>', sep = '\n')
   },
   warning = function(x, options) {
     paste('\n\n<div class="alert alert-warning">',
           gsub('##', '\n', gsub('^##\ Warning:', '**Warning**', x)),
           '</div>', sep = '\n')
   },
   message = function(x, options) {
     paste('\n\n<div class="alert alert-info">',
           gsub('##', '\n', x),
           '</div>', sep = '\n')
   }
)
```

```{r oneliners, error = TRUE}
stop('This should break!')
warning('Watch out!')
message('This is a message for you')
```

All this was achieved with the following knitr settings. Potentially, LaTeX templates could be written for PDF and Beamer output as well.

```{r ref.label = 'setup', echo = TRUE, eval = FALSE}
```

Notice the regular expressions, which replace the `## Error`/`## Warning` with bold text. (It is necessary to get rid of the hashes to avoid the text being turned into a level two (`<h2>`) header, but you could also adjust the `comment` chunk option.)
Is there a way of accessing the errors/warnings/messages before this stage for a more elegant solution?

What if the messages go onto multiple lines? The double `gsub` should take care of it.

```{r multiline, error = TRUE}
stop('This\nshould\nbreak!\n')
warning('Watch\nout!')
message('Let\nthat\nbe\na\nmessage')
```

A better solution, perhaps, might be to read carefully what is written at https://yihui.name/knitr/hooks/ and consider the `knitr::render_html()` function.
Doing things this way might also side-step the problem of writing conditional markup for the different output formats.

After a bit of research, the solution to the multi-line commenting problem appears to lie in the functions `knitr:::wrap.error`, `wrap.message` and `wrap.warning`. My idea is: just trick them into thinking that `options$comment` has been set to an empty string, and leave everything else the same.

```{r renderHTML, eval = FALSE}
wrap.error <- function(x, options) {
  options$comment <- ""
  knitr:::msg_wrap(paste(x$message, collapse = ""), "error", options)
}
wrap.message <- function(x, options) {
  options$comment <- ""
  knitr:::msg_wrap(paste(x$message, collapse = ""), "message", options)
}
wrap.warning <- function(x, options) {
  options$comment <- ""
  knitr:::msg_wrap(paste(x$message, collapse = ""), "warning", options)
}
```

But it is not easy, as far as I can tell, to replace non-exported S3 functions in packages, so short of forking the entire `knitr` package and rebuilding it with this file changed, the find-and-replace strategy will have to do.
