---
title: "Untitled"
format: html
editor: visual
---

```{css,echo=FALSE}

html, body {
  height: 100%;
}

body {
  display: grid;
  font: 400 145%/1.5 Verdana, sans-serif;
  place-items: center;
}

p {
  max-width: 30ch;
}

mark {
  -webkit-animation: 100s highlight 1.5s 1 normal forwards;
          animation: 30s highlight 1.5s 1 normal forwards;
  background-color: none;
  background: linear-gradient(90deg, #7efff5 50%, rgba(255, 255, 255, 0) 50%);
  background-size: 200% 100%;
  background-position: 100% 0;
}

@-webkit-keyframes highlight {
  0% {
    background-position: 100% 0;
  }
  30%, 70% {
    background-position: 0 0;
  }
  100% {
    background-position: -100% 0;
  }
}

@keyframes highlight {
  0% {
    background-position: 100% 0;
  }
  30%, 70% {
    background-position: 0 0;
  }
  100% {
    background-position: -100% 0;
  }
}
```



## Quarto

Quarto enables <mark>you to weave together content and executable code</mark>  into a finished document. To learn more about Quarto see <https://quarto.org>.

Cocoa lemon <mark>lime minty black beanwraps</mark> heat dark chocolate scotch bonnet pepper cayenne. <mark>Cozy butternut balsamic</mark> vinaigrette banana chocolate peanut butter.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
