---
title: "Pacote para colocar videos no Rmardown e Shiny"
author: "Steven Dutt Ross"
date: "17 de outubro de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#devtools::install_github("ijlyttle/vembedr")
#http://ijlyttle.github.io/vembedr/
```
Examples

For these examples, it can be useful to load the htmltools package along with the vembedr package.
```{r}
library("htmltools")
library("vembedr")
```
With the function embed_url(), you can use the URL from your browser to embed video:
```{r}
embed_url("https://www.youtube.com/watch?v=uV4UpCq2azs")
```


```{r}
embed_youtube("1-vcErOPofQ")
```

```{css}
.vembedr {
  display: inline-block;
  border-radius: 25px; /* adjust it to your needs */
  overflow: hidden;
}

.vembedr iframe {
  display: block;
  border: none;
}
```


```{r}
embed_vimeo("189919038") %>%
  div(class = "vembedr") %>%
  div(align = "center")
```


```{r}
embed_user2017("Room-202-Lightning-Talks") %>% 
  use_start_time("26m35s")
```

Note for GitHub README and RStudio viewer

The GitHub Markdown renderer does not support video embedding.

If you use the RStudio-IDE viewer to preview your work, please note that RStudio have made the design choice not to allow arbitrary external web-content in the IDE, which is wholly appropriate. However, with the advent of the learnr package, the IDE-viewer supports embedding of Vimeo and YouTube videos.

Otherwise, you can simply open your preview in an external browser