---
title: "Embed videos into your Rmarkdown"
author: "Steven Dutt Ross"
date: "28 de junho de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## vebmedr

The goal of the vembedr package is to make it a little bit easier for you to embed videos into your rmarkdown documents and your shiny apps. Three services are currently supported: YouTube, Vimeo, and Microsoft Channel 9 (including UseR! 2016 and 2017 videos).


## Installation

```{r, eval=FALSE}
#You can install the latest released version from CRAN with:
install.packages("vembedr")

#or the latest development version from GitHub with:
devtools::install_github("ijlyttle/vembedr")
```


With the function embed_url(), you can use the URL from your browser to embed video:

```{r}
library("htmltools")
library("vembedr")
embed_url("https://www.youtube.com/watch?v=UeMheG03w4s")

```

```{r}
suggest_embed("https://www.youtube.com/watch?v=UeMheG03w4s?t=1m32s")
```

To embed a YouTube (or Vimeo, or Channel 9) video you can use its identifier, which you can get from the original URL.

```{r}
embed_youtube("UeMheG03w4s?t=1m32s")

```


```{css}
.vembedr {
  display: inline-block;
  border-radius: 25px; /* adjust it to your needs */
  overflow: hidden;
}

.vembedr iframe {
  display: block;
  border: none;
}
```



To embed a Vimeo with some custom formatting:

    call embed_vimeo() using the Vimeo identifier, then
    wrap that in <div/> using our new vembedr class, then
    wrap that in a <div/> that centers its contents

```{r}
embed_vimeo("189919038") %>%
  div(class = "vembedr") %>%
  div(align = "center")

```


ou can also specify a start time. Please note that for Vimeo, specifying a start time implies that the video will be auto-played (which can be annoying).

Here’s an example using a lightning presentation from UseR!2017:

```{r}
embed_user2017("Room-202-Lightning-Talks") %>% 
  use_start_time("26m35s")

```

